Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-11 related.tex
editing related

The first class of methods is model oriented. These methods often include one of two things: Building local  models around points in a time series or analyzing statistics on the distribution of model errors. A few examples of the first case are \cite{Smith199250,dvsplots}, in \cite{Smith199250} for example they build local error distributions around "landmarks"(look up actual word they use) of a reconstructed trajectory of a dynamical system. They then use these distributions to predict error bounds on  predictions which occur within that $\epsilon$-ball. DVS-plots (Deterministic-vs-Stochastic plots) are somewhat similar to this

>>>>

The first class of methods is model oriented. These methods often include one of two things: Building local  models around points in a time series or analyzing statistics on the distribution of model errors. A few examples of the first case are \cite{Smith199250,Casdagli92dvsplots}, in \cite{Smith199250} for example they build local error distributions around "landmarks"(look up actual word they use) of a reconstructed trajectory of a dynamical system. They then use these distributions to predict error bounds on  predictions which occur within that $\epsilon$-ball. Casdagli introduced Deterministic-vs-Stochastic plots (DVS-plots) in \cite{Casdagli92dvsplots}
